NumLin: Linear Types for Linear Algebra

### 2018-11-01 write-up/paper/formal_system.tex
Add interpretation and proof

The full typing rules are in Appendix \label{subsec:static_sem}, but the key
ideas are as follow: \textsf{Perm}, \textsf{Type}, $\Theta, \Delta, \Gamma$,
value restriction, lambda, Gen/Spc, and Fix.

@@

\subsection{The logical relation}

>>>>

The full typing rules are in Appendix \ref{subsec:static_sem}, but the key
ideas are: \textsf{Perm}, \textsf{Type}, $\Theta, \Delta, \Gamma$,
value restriction, lambda, Gen/Spc, and Fix.

@@

\subsection{Logical Relation}

### 2018-11-01 write-up/paper/paper.tex
Sketch out Implementation section
Add points about finding bugs
Finish desugaring and matrix expression figures
Add Appendix and more figures
Add section on OCaml 'optimisation'
Add frac. perm. sub. lemma
Add Ott Semantics
Add interpretation and proof

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{hyperref}
\hypersetup{%
    colorlinks=true,
    linkcolor={black},
    citecolor={green}
}
\renewcommand\UrlFont{\color{blue}\rmfamily}

% Source code highlighting
\usepackage[outputdir=../build]{minted}
  % Magic incantation to stop minted from putting red boxes around shit
  \usepackage{etoolbox}
  \makeatletter
  \AtBeginEnvironment{minted}{\dontdofcolorbox}
  \def\dontdofcolorbox{\renewcommand\fcolorbox[4][]{##4}}
  \makeatother
\RecustomVerbatimEnvironment{Verbatim}{BVerbatim}{}

\newmintinline[highl]{ocaml}{breaklines}

\usepackage{amsmath}

@@

\title{NumLin: Linear Types for Numerical Libraries}

% \titlerunning{NumLin: Linear Types for Numerical Libraries}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here

@@

\institute{\email{dcm41@cam.ac.uk}
\url{dhruvmakwana.com} \and
Department of Computer Science, University of Cambridge\\
\email{nk480@cl.cam.ac.uk}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Briefly summarize the contents of the paper in 150--250 words.

\keywords{numerical, linear, algebra, types, permissions, OCaml}
\end{abstract}
%
%
%
\input{intro}

@@

>>>>

\documentclass[runningheads,a4paper,twoside]{llncs}
\usepackage{hyperref}
\hypersetup{%
    colorlinks=true,
    linkcolor={black},
    citecolor={black},
    urlcolor={blue}
}

% Source code highlighting
\usepackage[outputdir=../build]{minted}
  % Magic incantation to stop minted from putting red boxes around shit
  \usepackage{etoolbox}
  \makeatletter
  \AtBeginEnvironment{minted}{\dontdofcolorbox}
  \def\dontdofcolorbox{\renewcommand\fcolorbox[4][]{##4}}
  \makeatother
\RecustomVerbatimEnvironment{Verbatim}{BVerbatim}{}
% Convenient inline syntax highlighting
\newmintinline[highl]{ocaml}{breaklines}

\usepackage{amsmath,amssymb}

% Ott Rules
\usepackage{supertabular}%
\usepackage[margin=1in]{geometry}%
\usepackage{ifthen}%
\usepackage{alltt}%hack%

\input{../semantics/semantics_def}%
\usepackage{ottlayout}%
\renewcommand{\ottpremise}[1]{\premiseSTY{#1}}%
\renewcommand{\ottusedrule}[1]{\usedruleSTY{#1}}%
\renewcommand{\ottdrule}[4][]{\druleSTY[#1]{#2}{#3}{#4}}%
\renewenvironment{ottdefnblock}[3][]{\defnblockSTY[#1]{#2}{#3}}{\enddefnblockSTY}%

% Proof macros
\newcommand{\den}[3]{ \mathcal{#1}_{#2} [\![ #3 ]\!] }%
\newcommand{\V}[2]{ \den{V}{#1}{#2} }%
\newcommand{\C}[2]{ \den{C}{#1}{#2} }%

\newcommand{\Unit}{\ottkw{unit}}%
\newcommand{\Bang}{\ottkw{!}}
\newcommand{\Bool}{\ottkw{bool}}%
\newcommand{\Int}{\ottkw{int}}%
\newcommand{\Elt}{\ottkw{elt}}%
\newcommand{\Mat}{\ottkw{mat}}%
\newcommand{\Zf}{\ottkw{Z}}%
\newcommand{\Sf}{\ottkw{S}}%
\newcommand{\Many}{\ottkw{Many}}%
\newcommand{\dom}{\mathrm{dom}}%
\newcommand{\empH}{\emptyset}%

\usepackage{pf2}
\beforePfSpace{15pt, 10pt, 10pt, 10pt, 5pt, 2pt}
\afterPfSpace{15pt, 10pt, 10pt, 10pt, 5pt, 2pt}
\interStepSpace{15pt, 10pt, 10pt, 10pt, 5pt, 2pt}
\pflongindent%

% Multi-line table cells
% tex.stackexchange.com/questions/2441/how-to-add-a-forced-line-break-inside-a-table-cell#19678
\newcommand{\specialcell}[3][c]{%
  \begin{array}[#1]{@{}#2@{}}#3\end{array}}

\newcommand{\alsocell}[3][c]{%
  \begin{tabular}[#1]{@{}#2@{}}#3\end{tabular}}

% Figures
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{lscape}
\usepackage{pgfplots}

% PL Stuff
\usepackage[nounderscore]{syntax}
\renewcommand{\syntleft}{\normalfont\itshape}
\renewcommand{\syntright}{}
\renewcommand{\ulitleft}{\normalfont\bf}%\syn@ttspace\frenchspacing}
\renewcommand{\ulitright}{}
\renewcommand{\litleft}{\bgroup\ulitleft}
\renewcommand{\litright}{\ulitright\egroup}

@@

\title{NumLin: Linear Types for Linear Algebra}

% \titlerunning{NumLin: Linear Types for Linear Algebra}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here

@@

\institute{\email{dcm41@cam.ac.uk}
\url{dhruvmakwana.com} \and
Department of Computer Science, University of Cambridge\\
\email{nk480@cl.cam.ac.uk}}
%
\maketitle
%
\begin{abstract}
Briefly summarize the contents of the paper in 150--250 words.
%
\keywords{numerical, linear, algebra, types, permissions, OCaml}
\end{abstract}

\input{intro}

@@

\appendix
\input{appendix}
